Bioinformatics Midterm

### 2016-02-08 bioinformatics/latex/midterm.tex
add stufffff
Add changes to midterm.

>>>>

\section{Four: BLAST flubber}

\textbf{A.)} blastall -p blastp -i flubber.fasta -o flubber\_blast.txt\\
\textbf{B.)} The top his is for protein FluB of \textit{Actinomadura vulgaris}.
The highest scoring alignment has a score of 754, the total score is 1213 and the
E-value is 0.\\
\textbf{C.)} E-value calculation:

\begin{align*}
  E &= Knme^{-\lambda S}\\
  &= K(2.5*10^{10})(417)e^{-\lambda * 1213}\\
\end{align*}

\section{Five: MEME commands}

Check this with the homework on your desk and online if possible

\textbf{A.)} meme peptides.fasta -protein -mod anr -minw 7 -maxw 7\\
\textbf{B.)} meme enhancers.fa -dna -mod oops -maxw 10\\

\section{Six: blastall commands}
\textbf{A.)} formatdb -p F -t midichlorians -n midichlorians -i yoda.microbiome.fasta\\
\textbf{B.)} blastall -p blastp -i transcripts.fa -d myProteins  -g 2 -o transcripts.txt # gap pen rite??\\
\textbf{C.)} blastall -p blastp -i proteins.fa -d myGenome -o proteins.txt\\

\section{Eight: Revcomp GC}

from Bio import SeqIO

seq = Bio.Seq(``sequence'')
print ``Is GC content of sequence and sequence.revcomp equal?''
print seq.cg() == seq.revcomp.cg()

Then try it on sequence...

\section{Nine: }
